Concurrent Programming with CXL

### 2020-07-02 book/paper.tex
Latest

Unfortunately, if we run the program through CXL,
we find that the assertion still fails.
Figure~\ref{fig:naiveLockhtml} shows the CXL output.
Process~0 finds that the lock is available, but just before it stores
\texttt{True} in \textit{lockTaken} in instruction~9, process~1 gets
to run.  Because \textit{lockTaken} is still \texttt{False}, it too
believes it can acquire the lock, and stores \texttt{True} in
\texttt{lockTaken} and moves on to the critical section.
Finally, process~0 moves on, also stores \texttt{True} and also moves
into the critical section.  Process~0 is the one that detects the
problem.
The \textit{lockTaken} variable
suffers from the same problem as the \textit{count} variable
in Figure~\ref{fig:inc}: operations
on it consist of several instructions.  It is thus possible
for both processes to believe the lock is available and to obtain the lock
at the same time.

>>>>

Unfortunately, if we run the program through CXL,
we find that the assertion still fails.
Figure~\ref{fig:naiveLockhtml} shows the CXL output.
Process~0 finds that the lock is available, but just before it stores
\texttt{True} in \textit{lockTaken} in instruction~9, process~1 gets
to run.
(Recall that you can hover your mouse over a machine instruction in order
to see what it does.)
Because \textit{lockTaken} is still \texttt{False}, it too
believes it can acquire the lock, and stores \texttt{True} in
\texttt{lockTaken} and moves on to the critical section.
Finally, process~0 moves on, also stores \texttt{True} and also moves
into the critical section.  Process~0 is the one that detects the
problem.
The \textit{lockTaken} variable
suffers from the same problem as the \textit{count} variable
in Figure~\ref{fig:inc}: operations
on it consist of several instructions.  It is thus possible
for both processes to believe the lock is available and to obtain the lock
at the same time.
